Environmental stress drives plant and pollinator specialisation

### 2020-06-17 paper/manuscript.Rmd
Minor changes to Methods based on Chris' comments
Chris sugestions for the Methods

Our models performed relatively well.
The Bayesian R^2^ for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates that our models were able to capture a large proportion of the variability on the data. 
Overall, we found that environmental stress does not have a consistent effect across species. 
Indeed, when looking at the fixed effects, stress has virtually no relationship with the normalised degree—our metric of specialisation (Figure \@ref(fig:fig-conditional-effects)a). 
However, environmental stress was still an important predictor in our model. 
The difference in WAIC between our baseline model and the model that did not include environmental stress was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
This apparent discrepancy can be explained by the variability of the specialisation-stress relationship across species.

@@

For some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
Interestingly, the slope of this relationship was correlated with the species' specialisation intercept in the model (Figure \@ref(fig:fig-random-effects)b and c). The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`] (95% credible intervals shown within square brackets).
This correlation indicates that the slope of the stress-specialisation relationship was more likely to be positive for species with many partners under average stress conditions (and more likely to be negative for species fewer partners).
Recall that the model estimates the intercept of the number of partners for each species at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
Extrapolating to no-stress conditions this means that species that would interact with few partners under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with many partners are more likely to interact with fewer.

@@

The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] which indicates the importance of the local context when determining specialisation. 
The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] .

>>>>

Our models performed relatively well.
The Bayesian R^2^ for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates that our models were able to capture a large proportion of the variability on the data. 
Environmental stress was still an important predictor in our model. 
The difference in WAIC between our baseline model and the model that did not include environmental stress was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).

We found that some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
Interestingly, the slope of these relationships was correlated with the species' specialisation intercepts in the model (Figure \@ref(fig:fig-random-effects)b and c). The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`] (95% credible intervals shown within square brackets).
This correlation indicates that the slope of the stress-specialisation relationship was more likely to be positive for species with many partners under average stress conditions (and more likely to be negative for species fewer partners).
Recall that the model estimates the intercept of the number of partners for each species at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
Species that would interact with few partners  under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with many partners are more likely to interact with fewer.

The the variability of the specialisation-stress relationship across species was also evident when looking at overall patterns. 
We found that environmental stress does not have a consistent effect across species. 
Indeed, when looking at the fixed effects, stress has virtually no relationship with the normalised degree—our metric of specialisation (Figure \@ref(fig:fig-conditional-effects)a).

@@

@@

The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] which indicates the importance of the local context when determining specialisation. 
The standard deviation of the species intercepts was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] .
